Historical supply of timber harvest residues in west-central Alberta

### 2021-09-09 analysis/joinRatioBiomass.Rmd
sept 9

```{r stuff}
ratios <- read.csv(file = '../data/ratios.csv')
biomass <- read.csv(file = '../data/bioCalcOutput.csv') %>% select(-Province,-Height)
ratiosBiomass <- ratios %>% right_join(biomass,by=c("Ecozone","Genus","Species","Variety","DBH"))
ratiosBiomass <- ratiosBiomass %>% add_column(residueBiomass=0) %>% add_column(residueFactor=0)
ratiosBiomass$residueBiomass <- ratiosBiomass$branches + ratiosBiomass$foliage +
  (ratiosBiomass$topBarkRatio * ratiosBiomass$stem_bark) + 
  (ratiosBiomass$topVolRatio * ratiosBiomass$stem_wood)
ratiosBiomass$residueFactor <- ratiosBiomass$residueBiomass / ratiosBiomass$merchVol / 1000
ratios
biomass
#ratiosBiomass
#ratiosBiomass %>% filter(Species == "TRE",DBH == 20)
ratiosBiomassBorealPlains <- ratiosBiomass %>% filter(Ecozone == 9, Species == "BAN" | Species == "CON" | Species ==  "GLA" | Species ==  "MAR" | Species == "TRE")
ratiosBiomassBorealPlains

>>>>

```{r stuff}
ratios <- read.csv(file = '../data/ratios.csv')
biomass <- read.csv(file = '../data/bioCalcOutput.csv') %>% select(-Province,-Height)
ratiosBiomass <- ratios %>% right_join(biomass,by=c("Ecozone","Genus","Species","Variety","DBH"))
ratiosBiomass <- ratiosBiomass %>% add_column(residueBiomass=0) %>% add_column(residueFactor=0)
ratiosBiomass$residueBiomass <- ratiosBiomass$branches + ratiosBiomass$foliage +
  (ratiosBiomass$topBarkRatio * ratiosBiomass$stem_bark) + 
  (ratiosBiomass$topVolRatio * ratiosBiomass$stem_wood)
ratiosBiomass$residueFactor <- ratiosBiomass$residueBiomass / ratiosBiomass$merchVol / 1000
#ratios
#biomass
#ratiosBiomass
#ratiosBiomass %>% filter(Species == "TRE",DBH == 20)
ratiosBiomassBorealPlains <- ratiosBiomass %>% filter(Ecozone == 9, Species == "BAN" | Species == "CON" | Species ==  "GLA" | Species ==  "MAR" | Species == "TRE")
#ratiosBiomassBorealPlains

### 2021-09-09 analysis/manuscript.Rmd
sept 9

---
title: "Historical supply of timber harvest residues in west-central Alberta"
author:
- Alex McPhee^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
- Dennis Gray^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
- Glen W Armstrong^[Department of Renewable Resources, University of Alberta]
- Jay Anderson^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
date: "16/03/2021"
output:
  pdf_document:
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
  word_document:
  html_document:
    df_print: paged
bibliography: historicalResidueSupply.bib
---

@@

Here's something that might help our writing.  It's got the headings that *Biomass and Bioenergy* wants
and presents the main results based on our placeholder costs.  Author priority right now is alphabetical
based on our first names, or reverse alphabetical based on our last names.  This will likely change
based on contribution.

@@

  * four road classes

  * speeds by road class, loaded and unloaded

    * average speeds calculated using harmonic mean

@@

  * road network "rasterized" **how ?**

@@

  * median haul time calculated for each township

```{r haul, echo=FALSE, fig.cap="one way haul times from edson", out.width = '100%'}
knitr::include_graphics("../img/haultime.png")
```

@@

>>>>

---
title: "Historical supply of timber harvest residues in west-central Alberta"
author:

- Glen W Armstrong^[Department of Renewable Resources, University of Alberta]
- Jay Anderson^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
- Alex McPhee^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
date: "13/07/2021"
output:
  pdf_document:
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
  word_document:
  html_document:
    df_print: paged
bibliography: historicalResidueSupply.bib
---

@@

Here's something that might help our writing.  It's got the headings that *Biomass and Bioenergy* wants
and presents the main results based on our placeholder costs.  Author priority is not fixed.

@@

  * The provincial road network was sorted into four classes:

    * primary provincial highways

    * other paved roads

    * two-lane gravel roads

    * one-lane gravel or dirt roads

  * Average speeds calculated using harmonic mean:

@@

  * Speeds by road class, loaded and unloaded:

    * primary provincial highways: loaded 80, unloaded 95, h-mean 85

    * other paved roads: loaded 65, unloaded 80, h-mean 70

    * two-lane gravel roads: loaded 50, unloaded 70, h-mean 60

    * one-lane roads: loaded 20, unloaded 30, h-mean 25

@@

  * Rasterized network areas were generated using the QGIS plugin, QNEAT3 (Iso-Area as Interpolation).

  * QGIS zonal statistics were used to calculate the median network travel time in each township.

```{r haul, echo=FALSE, fig.cap="Alberta road network (left) and one-way haul time from Edson, limited to 6 hours.", out.width = '100%'}
knitr::include_graphics("../img/network_service.png")
```

@@

# Acknowledgements

Dennis Gray.  Future Energy Systems.
